### 2014-07-16 doc/thesis/cases.tex
Starting to port the current typing of the Lua Standard Libraries to its description file

@@

$\Top \times
(\String \cup \Nil) \times
\TopStar \rightarrow
\NilStar \cup
(\Top \times
(\String \cup \Nil) \times
\TopStar)$ 

@@

$(\String \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
(\Number \times \Nil \times \NilStar) \cup
(\Number \times \Number \times \NilStar) \cup
(\Boolean \times \Nil \times \NilStar)$

@@

\item $\Nil \times \TopStar \rightarrow \Number \times \NilStar$
\item $``collect" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``stop" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``restart" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``count" \times \TopStar \rightarrow \Number \times \Number \times \NilStar$
\item $``step" \times \TopStar \rightarrow \Boolean \times \NilStar$
\item $``setpause" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``setstepmul" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``isrunning" \times \TopStar \rightarrow \Boolean \times \NilStar$
\item $``generational" \times \TopStar \rightarrow \Number \times \NilStar$
\item $``incremental" \times \TopStar \rightarrow \Number \times \NilStar$

@@

$(\String \cup \Nil) \times
\TopStar \rightarrow
\AnyStar
$

@@

$\String \times
(0 \cup 1 \cup 2 \cup \Nil) \times
\TopStar \rightarrow
\NilStar$
\item \_G : $\{ \String:\Top \}$

@@

$\mu X.\{ \_\_metatable:\Top \} \times
\TopStar \rightarrow
(\Nil \cup \{ \_\_metatable:\Top \}) \times
\NilStar$

@@

$\{ \Number:\Any \} \times
\TopStar \rightarrow
\Number \times
\Any \times
\NilStar$

@@

\item Will $\{ ``tag":\String,\; \Number:\Any \}$ type check?

@@

$(\String \cup (\TopStar \rightarrow \TopStar)) \times
(\String \cup \Nil) \times
(``b" \cup ``t" \cup ``bt" \cup \Nil) \times
(\Top \cup \Nil) \times
\TopStar \rightarrow
((\TopStar \rightarrow \TopStar) \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$

@@

$(\String \cup \Nil) \times
(``b" \cup ``t" \cup ``bt" \cup \Nil) \times
(\Top \cup \Nil) \times
\TopStar \rightarrow
((\TopStar \rightarrow \TopStar) \times \NilStar) \cup
(\Nil \times \String \times \NilStar)$

@@

$\{ \Any:\Any \} \times
(\Any \cup \Nil) \times
\TopStar \rightarrow
(\Nil \times \NilStar) \cup
(\Any \times \Any \times \NilStar)$

@@

$\{ \Any:\Any \} \times
\TopStar \rightarrow
\Any \times 
\Any \times
\NilStar$

@@

$(\TopStar \rightarrow \TopStar) \times
\TopStar \rightarrow
(\Boolean \times \AnyStar) \cup
(\Boolean \times \String \times \NilStar)$
\item print (···) : $\TopStar \rightarrow \NilStar$

@@

$\Top \times
\Top \times
\TopStar \rightarrow
\Boolean \times
\NilStar$

@@

$\{ \Top:\Top \} \times
\Top \times
\TopStar \rightarrow
\Any \times
\NilStar$

@@

$(\{ \Top:\Top \} \cup \String) \times
\TopStar \rightarrow
\Number \times
\NilStar$

@@

$\{ \Top:\Top \} \times
\Top \times
\Top \times
\TopStar \rightarrow
\{ \Any:\Any \} \times
\NilStar$

@@

$\Number \times
\AnyStar \rightarrow
\AnyStar$

@@

$\String \times \AnyStar \rightarrow \Number \times \NilStar$

@@

$\{ \Top:\Top \} \times
(\Nil \cup \{ \_\_index:\mu X.\{ \Top:\Top \} \}) \times
\TopStar \rightarrow
\{ \_\_index:\mu X.\{ \Top:\Top \} \} \times
\NilStar$

@@

@@

$\String \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$

@@

$\Top \times
\TopStar \rightarrow
\String \times
\NilStar$

@@

$\Top \times
\TopStar \rightarrow
(``nil" \cup
``number" \cup
``string" \cup
``boolean" \cup
``table" \cup
``function" \cup
``thread" \cup
``userdata") \times
\NilStar$
\item \_VERSION : $\String$

@@

$(\TopStar \rightarrow \TopStar) \times
\Top \times
\TopStar \rightarrow
(\Boolean \times \AnyStar) \cup
(\Boolean \times \String \times \NilStar)$

@@

\subsection{String manipulation}

\begin{enumerate}
\item string.byte (s [, i [, j]]) :
$\String \times
(\Number \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\Number{*}$
\item string.char (···) :
$\Number{*} \rightarrow
\String \times
\NilStar$
\item string.dump (function) :
$(\TopStar \rightarrow \TopStar) \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.find (s, pattern [, init [, plain]]) :
$\String \times
\String \times
(\Number \cup \Nil) \times
(\Boolean \cup \Nil) \times
\TopStar \rightarrow
(\Number \times \Number \times \NilStar) \cup
(\Nil \times \NilStar)$
\item string.format (formatstring, ···) :
$\String \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.gmatch (s, pattern) :
$\String \times
\String \times
\TopStar \rightarrow
\String{*}$
\\
This function actually returns an iterator,
so I still need to confirm its return type.
\item string.gsub (s, pattern, repl [, n]) :
$\String \times
\String \times
(\String \cup \{ \Top:\Top \} \cup (\TopStar \rightarrow \TopStar)) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\String \times
\Number \times
\NilStar$
\item string.len (s) :
$\String \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item string.lower (s) :
$\String \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.match (s, pattern [, init]) :
$\String \times
\String \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
(\String \times \String{*}) \cup
(\Nil \times \NilStar)$
\item string.rep (s, n [, sep]) :
$\String \times
\Number \times
(\String \cup \Nil) \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.reverse (s) :
$\String \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.sub (s, i [, j]) :
$\String \times
\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\String \times
\NilStar$
\item string.upper (s) :
$\String \times
\TopStar \rightarrow
\String \times
\NilStar$
\end{enumerate}

\subsection{Table manipulation}

\begin{enumerate}
\item table.concat (list [, sep [, i [, j]]]) :
$\{ \Number:\String \cup \Number \} \times
(\String \cup \Nil) \times
(\Number \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\String \times
\NilStar$
\item table.insert (list, [pos,] value) :
$\{ \Number:\Top \} \times
(\Number \times \Top) \cup
(\Top \times \Nil) \times
\TopStar \rightarrow
\NilStar$
\\
This function does not accept/discard extra parameters.
Perhaps due to the fact that the parameter \textbf{pos} is optional.
If \textbf{value} is $\TopStar$, the function inserts \textbf{pos}
in the \textbf{list}, that is, the input type is
$\{ \Number:\Top \} \times \Top \times \TopStar$.
If \textbf{value} is $\Nil$, the function does not insert \textbf{pos}
in the \textbf{list}, that is, the input type is
$\{ \Number:\Top \} \times \Number \times \Top \times \TopStar$,
but the element is not inserted in the list because $\Top$ is actually $\Nil$.
\item table.pack (···) :
$\TopStar \rightarrow
\{ \Number:\Top \} \times
\NilStar$
\\
Even though \textbf{table.pack} gets any number of parameters of
any type, the $\Nil$ type generates a hole in the returned table.
\item table.remove (list [, pos]) :
$\{ \Number:\Top \} \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Top \times
\NilStar
$
\\
The return type depends on the type of the element that is removed
from the list.
\item table.sort (list [, comp]) :
$\{ \Number:\Top \} \times
((\TopStar \rightarrow \TopStar) \cup \Nil) \times
\TopStar \rightarrow
\NilStar$
\item table.unpack (list [, i [, j]]) :
$\{ \Number:\Top \} \times
(\Number \cup \Nil) \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\TopStar$
\\
The return type depends on the type of the elements that are stored in
the list.
\end{enumerate}

\subsection{Mathematical functions}

\begin{enumerate}
\item math.abs (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.acos (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.asin (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.atan (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.atan2 (y, x) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.ceil (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.cos (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.cosh (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$  
\item math.deg (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.exp (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.floor (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.fmod (x, y) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.frexp (x) :
$\Number \times \TopStar \rightarrow \Number \times \Number \times \NilStar$
\item math.huge : $\Number$
\item math.ldexp (m, e) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.log (x [, base]) :
$\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item math.max (x, ···) :
$\Number \times \Number{*} \rightarrow \Number \times \NilStar$
\item math.min (x, ···) :
$\Number \times \Number{*} \rightarrow \Number \times \NilStar$
\item math.modf (x) :
$\Number \times \TopStar \rightarrow \Number \times \Number \times \NilStar$
\item math.pi : $\Number$
\item math.pow (x, y) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.rad (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.random ([m [, n]]) :
$(\Number \cup \Nil) \times
(\Number \cup \Nil) \rightarrow
\Number \times
\NilStar$
\\
This function does not accept $\Nil$ as its only parameter,
although the parameter passing is optional.
This function does not accept/discard extra parameters.
\item math.randomseed (x) :
$\Number \times \TopStar \rightarrow \NilStar$
\item math.sin (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.sinh (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.sqrt (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.tan (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item math.tanh (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\end{enumerate}

\subsection{Bitwise operations}

\begin{enumerate}
\item bit32.arshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.band (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.bnot (x) :
$\Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.bor (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.btest (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.bxor (···) :
$\Number{*} \rightarrow \Number \times \NilStar$
\item bit32.extract (n, field [, width]) :
$\Number \times
\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item bit32.replace (n, v, field [, width]) :
$\Number \times
\Number \times
\Number \times
(\Number \cup \Nil) \times
\TopStar \rightarrow
\Number \times
\NilStar$
\item bit32.lrotate (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.lshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.rrotate (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\item bit32.rshift (x, disp) :
$\Number \times \Number \times \TopStar \rightarrow \Number \times \NilStar$
\end{enumerate}

>>>>

Categories:
\begin{enumerate}
\item Easy to type, because the current type system is enough.
\item Not easy to type, because it requires polymorphism.
\item Hard to type, because neither the current type system nor
      polymorphism are enough.
\end{enumerate}

@@

\begin{verbatim}
(any, string?) -> (any, string?) | (nil)
\end{verbatim}
Category 2?

@@

\begin{verbatim}
(string?, number?) -> (number) | (number, number) | (boolean)
\end{verbatim}
Category 3.

@@

\begin{verbatim}
() -> (number)
("collect") -> (number)
("stop") -> (number)
("restart") -> (number)
("count") -> (number, number)
("step") -> (boolean)
("setpause") -> (number)
("setstepmul") -> (number)
("isrunning") -> (boolean)
("generational") -> (number)
("incremental") -> (number)
\end{verbatim}

@@

\begin{verbatim}
(string?) -> (any*)
\end{verbatim}
Category 3?

@@

\begin{verbatim}
(string, number?) -> ()
\end{verbatim}
Category 1.
\item \_G :
\begin{verbatim}
{string:any}
\end{verbatim}
Category 3?

@@

\begin{verbatim}
(any) -> (any?)
\end{verbatim}
Category 3.

@@

\begin{verbatim}
({any}) -> ((any*) -> (any*)
\end{verbatim}
Category 3.

@@

\item Will \texttt{\{"tag":string, number:any\}} type check?

@@

\begin{verbatim}
(string|(any*) -> (any*), string?, string?, any?) ->
((any*) -> (any*))?
\end{verbatim}
Category 3?
I guess the proper type should be:
\begin{verbatim}
(string|(any*) -> (any*)) |
(string|(any*) -> (any*), string) |
(string|(any*) -> (any*), string, string, any?) ->
((any*) -> (any*))?
\end{verbatim}

@@

\begin{verbatim}
(string?, string?, any?) -> ((any*) -> (any*))?
\end{verbatim}
Category 3?
I guess the proper type should be:
\begin{verbatim}
() | (string) | (string, string) | (string, string, any?) ->
((any*) -> (any*))?
\end{verbatim}

@@

\begin{verbatim}
({any:any}, any?) -> (any, any) | (nil)
\end{verbatim}
Category 2.

@@

\begin{verbatim}
({any}) -> ((any*) -> (any*)
\end{verbatim}
Category 3.

@@

\begin{verbatim}
((any*) -> (any*), any*) -> (true, any*) | (false, string)
\end{verbatim}
Category 3?
\item print (···) :
\begin{verbatim}
(value*) -> ()
\end{verbatim}
Category 1.

@@

\begin{verbatim}
(value, value) -> (boolean)
\end{verbatim}
Category 2.

@@

\begin{verbatim}
({}, any) -> (any)
\end{verbatim}
Category 2.

@@

\begin{verbatim}
({}|string) -> (number)
\end{verbatim}
Category 1.

@@

\begin{verbatim}
({any:any}, any, any) -> ({any:any})
\end{verbatim}
Category 3.

@@

\begin{verbatim}
(number, any*) -> (any*)
\end{verbatim}
Category 3.

@@

\begin{verbatim}
(string, any*) -> (number)
\end{verbatim}

@@

\begin{verbatim}
({any:any}, {any:any}|nil) -> ({any:any}) 
\end{verbatim}
Category 3.

@@

This function is a primitive in the type system.

@@

\begin{verbatim}
(value, number|string?) -> (number) | (nil)
\end{verbatim}
Category 3.
The type of \textbf{base} depends on the type of \textbf{e}:
\begin{verbatim}
(value) -> (number) | (nil)
(string, number|string) -> (number) | (nil)
\end{verbatim}

@@

\begin{verbatim}
(value) -> (string)
\end{verbatim}
Category 1.

@@

\begin{verbatim}
(value) ->
("nil"|"number"|"string"|"boolean"|"table"|"function"|"thread"|"userdata")
\end{verbatim}
Category 1.
This function is a primitive in the type system.
\item \_VERSION :
\begin{verbatim}
string
\end{verbatim}
Category 1.

@@

\begin{verbatim}
((any*) -> (any*), any, any*) -> (true, any*) | (false, string)
\end{verbatim}
Category 3?

@@

\subsection{String Manipulation}

\begin{enumerate}
\item string.byte (s [, i [, j]]) :
\begin{verbatim}
(string, number?, number?) -> (number*)
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
(string) |
(string, number, number?) -> (number*)
\end{verbatim}
\item string.char (···) :
\begin{verbatim}
(number*) -> (string)
\end{verbatim}
Category 1.
\item string.dump (function) :
\begin{verbatim}
((value*) -> (value*)) -> (string)
\end{verbatim}
Category 3?
\item string.find (s, pattern [, init [, plain]]) :
\begin{verbatim}
(string, string, number?, true?) -> (number, number) | (nil)
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
(string, string) |
(string, string, number, true?) -> (number, number) | (nil)
\end{verbatim}
\item string.format (formatstring, ···) :
\begin{verbatim}
(string, any*) -> (string)
\end{verbatim}
Category 1.
\item string.gmatch (s, pattern) :
\begin{verbatim}
(string, string) -> ((any*) -> (any*))
\end{verbatim}
Category 3.
\\
This function actually returns an iterator,
so I still need to confirm its return type.
\item string.gsub (s, pattern, repl [, n]) :
\begin{verbatim}
(string, string, string|{}|(any*) -> (any*), number?) ->
(string, number)
\end{verbatim}
Category 1.
\item string.len (s) :
\begin{verbatim}
(string) -> (number)
\end{verbatim}
Category 1.
\item string.lower (s) :
\begin{verbatim}
(string) -> (string)
\end{verbatim}
Category 1.
\item string.match (s, pattern [, init]) :
\begin{verbatim}
(string, string, number?) -> (string, string*) | (nil)
\end{verbatim}
Category 1.
\item string.rep (s, n [, sep]) :
\begin{verbatim}
(string, number, string?) -> (string)
\end{verbatim}
Category 1.
\item string.reverse (s) :
\begin{verbatim}
(string) -> (string)
\end{verbatim}
Category 1.
\item string.sub (s, i [, j]) :
\begin{verbatim}
(string, number, number?) -> (string)
\end{verbatim}
Category 1.
\item string.upper (s) :
\begin{verbatim}
(string) -> (string)
\end{verbatim}
Category 1.
\end{enumerate}

\subsection{Table Manipulation}

\begin{enumerate}
\item table.concat (list [, sep [, i [, j]]]) :
\begin{verbatim}
({string|number}, string?, number?, number?) -> (string)
\end{verbatim}
Category 1.
\\
I guess the proper type should be:
\begin{verbatim}
({string|number}) |
({string|number}, string) |
({string|number}, string, number?) -> (string)
\end{verbatim}
\item table.insert (list, [pos,] value) :
\begin{verbatim}
({any}, any) -> ()
\end{verbatim}
Category 2.
\\
This function does not accept/discard extra parameters.
Perhaps due to the fact that the parameter \textbf{pos} is optional.
If \textbf{value} is $\TopStar$, the function inserts \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, any) -> ()}.
If \textbf{value} is $\Nil$, the function does not insert \textbf{pos}
in the \textbf{list}, that is, the input type is
\texttt{(\{any\}, number, any) -> ()},
but the element is not inserted in the list because \textbf{value}
is actually $\Nil$.
I guess the proper type should be:
\begin{verbatim}
({any}, any) | ({any}, number, any) -> ()
\end{verbatim}
\item table.pack (···) :
\begin{verbatim}
(any*) -> ({number:any, "n":number})
\end{verbatim}
Category 2.
\\
Even though \textbf{table.pack} gets any number of parameters of
any type, the $\Nil$ type generates a hole in the returned table.
\item table.remove (list [, pos]) :
\begin{verbatim}
({any}, number?) -> (any)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the element that is removed
from the list.
\item table.sort (list [, comp]) :
\begin{verbatim}
({any}, any?) -> ()
\end{verbatim}
Category 2.
\\
The proper type should be:
\begin{verbatim}
({any}, (any, any) -> (boolean)?) -> ()
\end{verbatim}
But there is a syntactic conflict for defining optional function types
that should be fixed in the parser.
\item table.unpack (list [, i [, j]]) :
\begin{verbatim}
({any}, number?, number?) -> (any*)
\end{verbatim}
Category 2.
\\
The return type depends on the type of the elements that are stored in
the list.
I guess the proper type should be:
\begin{verbatim}
({any}) | ({any}, number, number?) -> (any*)
\end{verbatim}
\end{enumerate}

\subsection{Mathematical Functions}

\begin{enumerate}
\item math.abs (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.acos (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.asin (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.atan (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.atan2 (y, x) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item math.ceil (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.cos (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.cosh (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.deg (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.exp (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.floor (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.fmod (x, y) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item math.frexp (x) :
\begin{verbatim}
(number) -> (number, number)
\end{verbatim}
Category 1.
\item math.huge :
\begin{verbatim}
number
\end{verbatim}
Category 1.
\item math.ldexp (m, e) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item math.log (x [, base]) :
\begin{verbatim}
(number, number?) -> (number)
\end{verbatim}
Category 1.
\item math.max (x, ···) :
\begin{verbatim}
(number, number*) -> (number)
\end{verbatim}
Category 1.
\item math.min (x, ···) :
\begin{verbatim}
(number, number*) -> (number)
\end{verbatim}
Category 1.
\item math.modf (x) :
\begin{verbatim}
(number) -> (number, number)
\end{verbatim}
Category 1.
\item math.pi :
\begin{verbatim}
number
\end{verbatim}
Category 1.
\item math.pow (x, y) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item math.rad (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.random ([m [, n]]) :
\begin{verbatim}
(number?, number?) -> (number)
\end{verbatim}
Category 1.
\\
This function does not accept $\Nil$ as its only parameter,
although the parameter passing is optional.
This function does not accept/discard extra parameters.
I guess the proper type should be:
\begin{verbatim}
() | (number, number?) -> (number)
\end{verbatim}
\item math.randomseed (x) :
\begin{verbatim}
(number) -> ()
\end{verbatim}
Category 1.
\item math.sin (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.sinh (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.sqrt (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.tan (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item math.tanh (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\end{enumerate}

\subsection{Bitwise Operations}

\begin{enumerate}
\item bit32.arshift (x, disp) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item bit32.band (···) :
\begin{verbatim}
(number*) -> (number)
\end{verbatim}
Category 1.
\item bit32.bnot (x) :
\begin{verbatim}
(number) -> (number)
\end{verbatim}
Category 1.
\item bit32.bor (···) :
\begin{verbatim}
(number*) -> (number)
\end{verbatim}
Category 1.
\item bit32.btest (···) :
\begin{verbatim}
(number*) -> (number)
\end{verbatim}
Category 1.
\item bit32.bxor (···) :
\begin{verbatim}
(number*) -> (number)
\end{verbatim}
Category 1.
\item bit32.extract (n, field [, width]) :
\begin{verbatim}
(number, number, number?) -> (number)
\end{verbatim}
Category 1.
\\
Should it be?
\begin{verbatim}
(number, 0|...|31, 1|...|32|nil) -> (number)
\end{verbatim}
\item bit32.replace (n, v, field [, width]) :
\begin{verbatim}
(number, number, number, number?) -> (number)
\end{verbatim}
Category 1.
\\
Should it be?
\begin{verbatim}
(number, number, 0|...|31, 1|...|32|nil) -> (number)
\end{verbatim}
\item bit32.lrotate (x, disp) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item bit32.lshift (x, disp) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item bit32.rrotate (x, disp) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\item bit32.rshift (x, disp) :
\begin{verbatim}
(number, number) -> (number)
\end{verbatim}
Category 1.
\end{enumerate}
